Highlighting Disputed Claims on the Web

### 2010-03-07 papers/wicow_claimfinder/wicow18e-ennals.tex
Trying to improve claim quality. Improved search engine entailment. Final versions of papers

% mendelybib is the bibliograph from our shared mendely space and is auto-generated
% localbib is used for manually adding anything we don't want to add to mendeley, particularly for
% people who are not mendeley users
\bibliography{mendeleybib,localbib}

>>>>

% mendelybib is the bibliograph from our shared mendely space and is auto-generated
% localbib is used for manually adding anything we don't want to add to mendeley, particularly for
% people who are not mendeley users

\begin{thebibliography}{10}

\bibitem{Adler2008b}
B~Thomas Adler, Krishnendu Chatterjee, Luca~De Alfaro, Marco Faella, Ian Pye,
  and Vishwanath Raman.
\newblock {Assigning Trust to Wikipedia Content}.
\newblock In {\em WikiSym}, 2008.

\bibitem{Banko2008}
M.~Banko, O.~Etzioni, and T.~Center.
\newblock {The tradeoffs between open and traditional relation extraction}.
\newblock In {\em Proceedings of the 46th Annual Meeting of the Association for
  Computational Linguistics (ACL-08)}, 2008.

\bibitem{Bird2009}
Steven Bird, Ewan Klein, and Edward Loper.
\newblock {\em {Natural Language Processing with Python}}.
\newblock O'Reilly, 2009.

\bibitem{Blumenstock2008}
Joshua~E Blumenstock.
\newblock {Size Matters: Word Count as a Measure of Quality on Wikipedia}.
\newblock {\em Computing}, pages 2007--2008, 2008.

\bibitem{Caraballo2001}
Sharon Caraballo.
\newblock {\em {Automatic construction of a hypernym-labeled noun hierarchy
  from text Sharon A. Caraballo}}.
\newblock Phd, Brown University, 2001.

\bibitem{Condoravdi2003}
Cleo Condoravdi, Dick Crouch, Valeria de~Paiva, Reinhard Stolle, and Daniel~G.
  Bobrow.
\newblock {Entailment, intensionality and text understanding}.
\newblock In {\em Proceedings of the HLT-NAACL 2003 workshop on Text meaning
  -}, pages 38--45, Morristown, NJ, USA, 2003. Association for Computational
  Linguistics.

\bibitem{Custard2005}
Myra Custard and Tamara Sumner.
\newblock {Using Machine Learning to Support Quality Judgements}.
\newblock {\em D-Lib Magazine}, 11(10), 2005.

\bibitem{Dawkins2006}
Richard Dawkins.
\newblock {\em {The God Delusion}}.
\newblock Houghton Mifflin Harcourt, 2006.

\bibitem{deMarneffe2008}
M.C. de~Marneffe, A.N. Rafferty, and C.D. Manning.
\newblock {Finding contradictions in text}.
\newblock In {\em Proceedings of the 46th Annual Meeting of the Association for
  Computational Linguistics (ACL-08)}, 2008.

\bibitem{duda}
R.~O. Duda, P.~E. Hart, and D.~G. Stork.
\newblock {\em Pattern Classification}.
\newblock Wiley-Interscience Publication, 2000.

\bibitem{Ennals2010}
Rob Ennals, Beth Trushkowsky, John~Mark Agosta, Tye Rattenbury, and Tad Hirsch.
\newblock {Highlighting Disputed Claims on the Web}.
\newblock In {\em Proceedings of the 19th international conference on World
  Wide Web - WWW 2010}, 2010.

\bibitem{Etzioni2008}
Oren Etzioni, Michele Banko, Stephen Soderland, and Daniel~S Weld.
\newblock {Open information Extraction from the Web}.
\newblock {\em Communications of the ACM}, 51(12), 2008.

\bibitem{Fogg2003}
B~J Fogg, Persuasive~Technology Lab, Cordura Hall, Cathy Soohoo, David~R
  Danielson, Ellen~R Tauber, Sliced~Bread Design, Mountain View, Julianne
  Stanford, Leslie Marable, and Consumer Webwatch.
\newblock {How Do Users Evaluate the Credibility of Web Sites? A Study with
  Over 2,500 Participants}.
\newblock {\em World Wide Web Internet And Web Information Systems}, pages
  1--15, 2003.

\bibitem{Giampiccolo2007}
D.~Giampiccolo, B.~Magnini, I.~Dagan, and B.~Dolan.
\newblock {The third pascal recognizing textual entailment challenge}.
\newblock In {\em Proceedings of the ACL-PASCAL Workshop on Textual Entailment
  and Paraphrasing}, number June, page 1–9, 2007.

\bibitem{Girju2003}
Roxana Girju, Adriana Badulescu, and Dan Moldovan.
\newblock {Learning semantic constraints for the automatic discovery of
  part-whole relations}.
\newblock In {\em Proceedings of HLT/NAACL}, volume~3, 2003.

\bibitem{Harabagiu2006}
S.~Harabagiu, A.~Hickl, and F.~Lacatusu.
\newblock {Negation, contrast and contradiction in text processing}.
\newblock In {\em Proceedings of the National Conference on Artificial
  Intelligence}, volume~21, page 755. Menlo Park, CA; Cambridge, MA; London;
  AAAI Press; MIT Press; 1999, 2006.

\bibitem{Hearst1992}
Marti~a. Hearst.
\newblock {Automatic acquisition of hyponyms from large text corpora}.
\newblock In {\em Computational linguistics}, Morristown, NJ, USA, 1992.
  Association for Computational Linguistics.

\bibitem{Hu2004}
Minqing Hu and Bing Liu.
\newblock {Mining and summarizing customer reviews}.
\newblock {\em Proceedings of the 2004 ACM SIGKDD international conference on
  Knowledge discovery and data mining - KDD '04}, page 168, 2004.

\bibitem{jones99bootstrapping}
Rosie Jones, Andrew McCallum, Kamal Nigam, and Ellen Riloff.
\newblock Bootstrapping for text learning tasks.
\newblock In {\em IJCAI-99 Workshop on Text Mining: Foundations, Techniques and
  Applications}, 1999.

\bibitem{Kawahara2008}
Daisuke Kawahara, Sadao Kurohashi, and Kentaro Inui.
\newblock {Grasping Major Statements and Their Contradictions Toward
  Information Credibility Analysis of Web Contents}.
\newblock {\em 2008 IEEE/WIC/ACM International Conference on Web Intelligence
  and Intelligent Agent Technology}, pages 393--397, 2008.

\bibitem{Kittur2009}
Aniket Kittur, Ed~H Chi, and Bongwon Suh.
\newblock {What's in Wikipedia? Mapping Topics and Conflict Using Socially
  Annotated Category Structure}.
\newblock In {\em CHI}, pages 1509--1512, 2009.

\bibitem{Backstrom2009}
Jure Lescovec, Lars Backstrom, and Jon Kleinberg.
\newblock {Meme-tracking and the Dynamics of the News Cycle}.
\newblock 2009.

\bibitem{mccallum98comparison}
A.~McCallum and K.~Nigam.
\newblock A comparison of event models for naive bayes text classification,
  1998.

\bibitem{Mihalcea2007}
Rada Mihalcea and Andras Csomai.
\newblock {Wikify! Linking Documents to Encyclopedic Knowledge}.
\newblock In {\em CIKM}, pages 233--241, 2007.

\bibitem{Murakami2009}
Koji Murakami, Eric Nichols, Suguru Matsuyoshi, Asuka Sumida, Shouko Masuda,
  Kentaro Inui, and Yuji Matsumoto.
\newblock {Statement Map: Assisting Information Credibility Analysis by
  Visualizing Arguments}.
\newblock In {\em Workshop on Information Credibility on the Web (WICOW)},
  2009.

\bibitem{Nadeau2007}
D.~Nadeau and S.~Sekine.
\newblock {A survey of named entity recognition and classification}.
\newblock {\em Linguisticae Investigationes}, 30(1), 2007.

\bibitem{Palmer.2001}
Frank~Robert Palmer.
\newblock {\em Mood and Modality}.
\newblock Cambridge Univesity Press, 2001.

\bibitem{Pang2004}
Bo~Pang and Lillian Lee.
\newblock {A Sentimental Education: Sentiment Analysis Using Subjectivity
  Summarization Based on Minimum Cuts}.
\newblock In {\em Proceedings of the Association for Computational
  Linguistics}, 2004.

\bibitem{Riloff1993}
E.~Riloff.
\newblock {Automatically constructing a dictionary for information extraction
  tasks}.
\newblock In {\em Proceedings of the National Conference on Artificial
  Intelligence}, 1993.

\vfill\eject

\bibitem{Ritter}
Alan Ritter, Doug Downey, Stephen Soderland, and Oren Etzioni.
\newblock {It's a Contradiction - No, it's Not: A Case Study using Functional
  Relations}.
\newblock In {\em Proceedings of the Conference on Empirical Methods in Natural
  Language Processing}, 2008.

\bibitem{Sahami98abayesian}
Mehran Sahami, Susan Dumais, David Heckerman, and Eric Horvitz.
\newblock A bayesian approach to filtering junk e-mail.
\newblock In {\em Proceedings of the AAAI'98 Workshop on Learning for Text
  Categorization}, 1998.

\bibitem{Shum2008}
Simon~Buckingham Shum.
\newblock {Cohere: Towards Web 2.0 Argumentation}.
\newblock In {\em Computational Models of Argument (COMMA)}, volume~44, 2008.

\bibitem{Snow2005}
R.~Snow, D.~Jurafsky, and A.Y. Ng.
\newblock {Learning syntactic patterns for automatic hypernym discovery}.
\newblock In {\em Advances in Neural Information Processing Systems},
  volume~17. Citeseer, 2005.

\bibitem{yahoo-boss}
Yahoo {BOSS}.
\newblock \url{http://developer.yahoo.com/search/boss/}.

\end{thebibliography}

### 2010-03-07 papers/www_disputefinder/wfp0406_ennals.tex
Trying to improve claim quality. Improved search engine entailment. Final versions of papers

\todo{Add count of disputed claims}

%\section{Acknowledgments}

\todo{Do we want to have acknowledgements}
% We would like to Thank Barbara Rosario for help with textual entailment, and 
% Acknowledgements omitted for blind submission. Dispute Finder uses icons from the free FamFamFam Silk\footnote{http://famfamfam.com} collection.

\todo{Sort out bad references}
\bibliography{refs}

>>>>

\begin{thebibliography}{10}

\bibitem{Adler2008a}
B~Thomas Adler and Ian Pye.
\newblock {Measuring Author Contributions to the Wikipedia ∗}.
\newblock In {\em WikiSym}, 2008.

\bibitem{Bayer2001}
S.~Bayer, J.~Burger, L.~Ferro, J.~Henderson, and A.~Yeh.
\newblock {MITRE’s Submissions to the EU Pascal RTE Challenge}.
\newblock In {\em PASCAL Challenge Workshop on Recognizing Textual Entailment}.
  Citeseer, 2005.

\bibitem{Bhagat2009}
R~Bhagat, E~Hovy, and S~Patwardhan.
\newblock {Acquiring paraphrases from text corpora}.
\newblock In {\em K-CAP}, 2009.

\bibitem{Bier2006}
Eric~A Bier, Edward~W Ishak, and Ed~Chi.
\newblock {Entity Workspace: an evidence file that aids memory, inference, and
  reading}.
\newblock In {\em Intelligence and Security Informatics}, 2006.

\bibitem{Bos2005}
Johan Bos and Katja Markert.
\newblock {Recognising textual entailment with logical inference}.
\newblock In {\em Human Language Technology and Empirical Methods in Natural
  Language Processing - HLT '05}, Morristown, NJ, USA, 2005. Association for
  Computational Linguistics.

\bibitem{Bouvin2000}
Niels~Olof Bouvin.
\newblock {Augmenting the Web through Open Hypermedia}.
\newblock {\em Phd Thesis, University of Aarhus}, 2000.

\bibitem{Conklin1987a}
Jeff Conklin and Michael~L Begeman.
\newblock {gIBIS: A Hypertext Tool for Team Design Deliberation}.
\newblock In {\em Hypertext}, 1987.

\bibitem{Braz}
R.~De~Salvo~Braz, R.~Girju, V.~Punyakanok, D.~Roth, and M.~Sammons.
\newblock {An inference model for semantic entailment in natural language}.
\newblock In {\em Artifical Intelligence}, volume~20. Springer, 2005.

\bibitem{Diakopoulos2008}
Nicholas Diakopoulos and Irfan Essa.
\newblock {An Annotation Model for Making Sense of Information Quality in
  Online Video}.
\newblock In {\em Pragmatic Web}, 2008.

\bibitem{Dinu2009}
Georgiana Dinu and Rui Wang.
\newblock {Inference Rules and their Application to Recognizing Textual
  Entailment}.
\newblock {\em Computational Linguistics}, pages 211--219, 2009.

\bibitem{Etzioni2008}
Oren Etzioni, Michele Banko, Stephen Soderland, and Daniel~S Weld.
\newblock {Open information Extraction from the Web}.
\newblock {\em Communications of the ACM}, 51, 2008.

\bibitem{Fogg2003}
B~J Fogg, Cathy Soohoo, David~R Danielson, Leslie Marable, Julianne Stanford,
  and Ellen~R Tauber.
\newblock {How Do Users Evaluate the Credibility of Web Sites? A Study with
  Over 2,500 Participants}.
\newblock In {\em CHI}, 2003.

\bibitem{Gil2002}
Y.~Gil and V.~Ratnakar.
\newblock {TRELLIS: An interactive tool for capturing information analysis and
  decision making}.
\newblock In {\em Knowledge Engineering and Knowledge Management}. Springer,
  2002.

\bibitem{Gil2006}
Yolanda Gil and Donovan Artz.
\newblock {Towards Content Trust of Web Resources}.
\newblock In {\em WWW}, pages 565--574, 2006.

\bibitem{Glickman2005}
O.~Glickman, I.~Dagan, and M.~Koppel.
\newblock {A probabilistic classification approach for lexical textual
  entailment}.
\newblock In {\em Artifical Intelligence}, volume~20. Menlo Park, CA;
  Cambridge, MA; London; AAAI Press; MIT Press; 1999, 2005.

\bibitem{Golder2006}
Scott~A Golder and Bernardo~A Huberman.
\newblock {The Structure of Collaborative Tagging Systems}.
\newblock {\em Journal of Information Science}, 2006.

\bibitem{Gordon1997}
Thomas~F Gordon and Nikos Karacapilidis.
\newblock {The Zeno Argumentation Framework}.
\newblock In {\em Artificial Intelligence and Law}, 1997.

\bibitem{Hearst1992}
Marti~a. Hearst.
\newblock {Automatic acquisition of hyponyms from large text corpora}.
\newblock In {\em Computational linguistics}, Morristown, NJ, USA, 1992.
  Association for Computational Linguistics.

\bibitem{Herman2002}
Edward~S Herman and Noam Chomsky.
\newblock {\em {Manufacturing Consent: The Political Economy of the Mass
  Media}}.
\newblock Pantheon, 2002.

\bibitem{Hong2009}
L.~Hong and E.H. Chi.
\newblock {Annotate once, appear anywhere: collective foraging for snippets of
  interest using paragraph fingerprinting}.
\newblock In {\em CHI}. ACM New York, NY, USA, 2009.

\bibitem{Isenmann1997}
Severin Isenmann and Wolf~D Reuter.
\newblock {IBIS - a Convincing Concept . . . But a Lousy Instrument?}
\newblock In {\em Designing Interactive Systems (DIS)}, 1997.

\bibitem{Jijkoun2006}
Valentin Jijkoun and Maarten~De Rijke.
\newblock {Recognizing Textual Entailment: Is Word Similarity Enough?}
\newblock In {\em Machine Learning Challenges}, 2006.

\bibitem{Koivunen2001}
Jose Kahan and Marja-Ritta Koivunen.
\newblock {Annotea: an open RDF infrastructure for shared Web annotations}.
\newblock In {\em WWW}, volume~39, 2002.

\bibitem{Kim2009}
Jong~Wook Kim.
\newblock {Ef cient Overlap and Content Reuse Detection in Blogs and Online
  News Articles}.
\newblock In {\em WWW}, 2009.

\bibitem{Kittur2008}
Aniket Kittur and Robert~E Kraut.
\newblock {Harnessing the Wisdom of Crowds in Wikipedia: Quality Through
  Coordination}.
\newblock {\em CSCW}, pages 37--46, 2008.

\bibitem{Kolak2008}
Okan Kolak and Bill~N Schilit.
\newblock {Generating Links by Mining Quotations}.
\newblock In {\em Hypertext}, 2008.

\bibitem{Backstrom2009}
Jure Lescovec, Lars Backstrom, and Jon Kleinberg.
\newblock {Meme-tracking and the Dynamics of the News Cycle}.
\newblock In {\em Knowledge Discovery and Data Mining (KDD)}, 2009.

\bibitem{Lin2001}
Dekang Lin and Patrick Pantel.
\newblock {DIRT – Discovery of Inference Rules from Text}.
\newblock In {\em Knowledge Discovery and Data Mining (KDD)}, 2001.

\bibitem{Manjou2008}
Farhad Manjou.
\newblock {\em {True Enough: Learning to Live in a Post-Fact Society}}.
\newblock Wiley, 2008.

\bibitem{Marlow2006}
Cameron Marlow, Mor Naaman, Danah Boyd, and Marc Davis.
\newblock {HT06, Tagging Paper, Taxonomy, Flickr, Academic Article, To Read}.
\newblock In {\em Hypertext}, 2006.

\bibitem{Olsen2004}
Dan~R Olsen, Trent Taufer, and Jerry~Alan Fails.
\newblock {ScreenCrayons: Annotating Anything}.
\newblock In {\em User Interface Software and Technology}, volume~6, 2004.

\bibitem{Park2009}
Souneil Park, Seungwoo Kang, Sangyoung Chung, and Junehwa Song.
\newblock {NewsCube: Delivering Multiple Aspects of News to Mitigate Media
  Bias}.
\newblock In {\em CHI}. Information Today, 2009.

\bibitem{PewResearch2008}
Pew Research.
\newblock {The Pew Research Center Biennial News Consumption Survey}, 2008.

\bibitem{Ritter}
Alan Ritter, Doug Downey, Stephen Soderland, and Oren Etzioni.
\newblock {It’s a Contradiction—No, it’s Not: A Case Study using
  Functional Relations}.
\newblock In {\em Empirical Methods in Natural Language Processing}, 2008.

\bibitem{Selvin2001}
Albert Selvin, Simon~Buckingham Shum, Maarten Sierhuis, Jeff Conklin, Beatrix
  Zimmermann, Charles Palus, Wilfred Drath, and David Horth.
\newblock {Compendium: Making Meetings into Knowledge Events}.
\newblock In {\em Knowledge Technologies}, 2001.

\bibitem{Sereno2004}
Bertrand Sereno, Simon Buckingham, and Enrico Motta.
\newblock {Semi-Automatic Annotation of Contested Knowledge on the World Wide
  Web}.
\newblock {\em WWW}, 2004.

\bibitem{Sereno2005}
Bertrand Sereno, Buckingham Shum, and Enrico Motta.
\newblock {ClaimSpotter: an Environment to Support Sensemaking with Knowledge
  Triples}.
\newblock In {\em Intelligent User Interfaces (IUI)}, 2005.

\bibitem{Shum2008}
Simon~Buckingham Shum.
\newblock {Cohere: Towards Web 2.0 Argumentation}.
\newblock In {\em Computational Models of Argument (COMMA)}, volume~44, 2008.

\bibitem{Snow2006}
Rion Snow, Lucy Vanderwende, and Arul Menezes.
\newblock {Effectively using syntax for recognizing false entailment}.
\newblock In {\em Human Language Technology}, Morristown, NJ, USA, 2006.
  Association for Computational Linguistics.

\bibitem{Theobald2008}
M.~Theobald, J.~Siddharth, and A.~Paepcke.
\newblock {Spotsigs: robust and efficient near duplicate detection in large web
  collections}.
\newblock In {\em SIGIR}. ACM, 2008.

\bibitem{Wiil1996}
Uffe~Kock Wiil and John~J Leggett.
\newblock {The HyperDisco Approach to Open Hypermedia Systems}.
\newblock In {\em Hypertext}, 1996.

\end{thebibliography}
